A Machine Learning Approach to MLB Catcher Framing

### 2021-12-09 Slides.Rmd
Add random forest

```{r setup, include=FALSE}
library(tidyverse)
library(gbm)
knitr::opts_chunk$set(echo = FALSE)
```

@@

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(gbm)
library(randomForest)
knitr::opts_chunk$set(echo = FALSE)
```

@@

## Random Forest

- 3 Fold Cross Validation on Random Forest  
  - Tested on nodesizes of 10, 30, 50, 70, 90 | 500 trees
  - Compared Out-Of-Bag Error 
```{r}
load("Data/pitchData.Rda")
load("Model-Outputs/random-forest.Rda")

ggplot(df_rf, aes(x = nodesize, y = accuracy))+
  geom_line() +
  geom_point() +
  geom_point(data = df_rf %>% 
               filter(accuracy == max(accuracy)), aes(x = nodesize, y = accuracy), color = "red") +
  ylim(0.925, 0.935) +
  labs(x = "Nodesize",
       y = "Accuracy",
       title = "Random Forest OOB Accuracy by Nodesize") +
  theme_minimal()
```
